Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-12-12 manuscript/manuscript.tex
Add values of b in exponential density

\begin{equation}
    \rho(r') = A e^{- \frac{b}{T} (r' - R)} + C,
\end{equation}

@@

\noindent $R$ is the mean Earth radius, $T$ is the thickness of the shell ($T = R_2
- R_1$) and $b$ is a dimensionless constant that determines the variability of the
function: a high value of $b$ increases the maximum slope of the density function.

>>>>

\begin{equation}
    \rho(r') = A e^{- \frac{b}{T} (r' - R)} + C,
    \label{eq:density-exp}
\end{equation}

@@

\noindent $R$ is the mean Earth radius, $T$ is the thickness of the shell ($T = R_2
- R_1$) and $b$ is a dimensionless constant that determines the variability of the
function: a higher value of $b$ increases the maximum slope of the density function.
On exponential density analysis we will use values of $b$ equal to 1, 2, 5, 10, 30
and 100, in order to cover different kind of exponential density variations, from smooth
to sharp.
